---
title: 'Homework 7: Automating Data-analysis Pipelines'
author: "Fariha Khan"
date: '2017-11-14'
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Fariha Khan
## Homework 7: Automating Data-analysis Pipelines

```{r }
suppressPackageStartupMessages(library(forcats))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(readr))
```

## Download Data
I initially downloaded the gapminder data using the download.file() function
```{r}
source('00_downloadData.R')
```

## Initial Analysis
I compared the life expectancy of each country by the year of the raw data.
I then reordered the data based on maximum life expectancy.
```{r}
source('01_cleanData.R')

old_levels
new_levels

print(plot1)
print(plot2)
```


### Top countries overview
I created a function to find the top 20 countries with the highest average life expectancy within each continent
```{r}
getTop20("Asia")
getTop20("Africa")
getTop20("Americas")
getTop20("Oceania")
getTop20("Europe")
```


## Top 3 countries Asia
I looked at the spread of the life expectancy for the top 3 countries for each continent (excluding Oceania).
```{r}
source('02_analyzeData.R')

kable(topAsia)
print(plot_tAsia)
```


## Top 3 countries Africa

```{r}
kable(topAfrica)
print(plot_tAfrica)
```

## Top 3 countries Americas

```{r}
kable(topAmericas)
print(plot_tAmericas)
```

## Top 3 countries Europe

```{r}
kable(topEurope)
print(plot_tEurope)
```